---
title: "hana Share data exploration "
resource_files:
- inc/Share_data.RData
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    theme: readable
    logo: inc/hana_logo_small.png
    css: inc/corp-styles.css
    includes:
      before_body: 'inc/google-analytics.js'
---

```{r setup, include=FALSE}
library(shiny)
library(flexdashboard)
library(dplyr)
library(tidyr)
library(readr)
library(stringr)
library(ggplot2)
library(plotly)
library(scales)
library(here)
library(rlang)
library(RColorBrewer)  
library(DT)
library(lubridate)
library(RiHana)

load('inc/Share_data.RData')




```

```{r}

updatedShareDataSummary <- reactive({
  share_data <-share_members_edited %>% 
    filter(earliest_start>=input$ShareTimeRange[1],
           earliest_start<=input$ShareTimeRange[2],
           grepl(input$FreePromoIntro,promo,ignore.case = TRUE),
           grepl(paste0(input$shareChannel,collapse="|"),acquisition_channel),
           grepl(paste0(input$hanaLocation,collapse="|"),hana_location)) %>% 
    summarise(total_members=n(),
              active_members=sum(still_active=='Yes'),
              rev_member=scales::dollar(sum(total_paid)/total_members))

  return(share_data)
})

updatedShareMonthlyChurn<- reactive({

  n_days <- interval(RiHana::get_relevant_date()$yoy_date,today())/days(1)
  cohort_dates<- tibble::enframe(RiHana::get_relevant_date()$yoy_date + days(0:n_days)) %>% 
  mutate(cohort_month=floor_date(value,unit="month"),
         end_month=ceiling_date(value,unit="month")-1) %>% 
  #group_by(cohort_month) %>% 
  select(cohort_month,end_month) %>% 
  unique(.) %>% 
  mutate(end_month=as_date(ifelse(end_month>RiHana::get_relevant_date()$yesterdays_date,RiHana::get_relevant_date()$yesterdays_date,end_month)))

  
  share_cohort_members<-share_members_edited %>% 
      filter(earliest_start>=input$ShareTimeRange[1],
           earliest_start<=input$ShareTimeRange[2],
           grepl(input$FreePromoIntro,promo,ignore.case = TRUE),
           grepl(paste0(input$shareChannel,collapse="|"),acquisition_channel),
           grepl(paste0(input$hanaLocation,collapse="|"),hana_location)) %>% 
    mutate(last_member_date=coalesce(latest_cancel,today()),
         join_cohort=floor_date(earliest_start,unit='month')) %>% 
    select(coworkerid,join_cohort,last_member_date)

monthly_churn<-cohort_dates %>% 
  fuzzyjoin::fuzzy_inner_join(.,share_cohort_members,by=c("cohort_month"="join_cohort","end_month"="last_member_date"),match_fun=list(`>=`,`<=`)) %>% 
  group_by(join_cohort,cohort_month) %>% 
  summarise(members=n()) %>% 
  mutate(period=row_number()) %>% 
  select(-cohort_month) %>% 
  group_by(join_cohort) %>% 
  mutate(prev_members=lag(members)) %>% 
  drop_na() %>% 
  ungroup(.) %>% 
  summarise(monthly_churn=scales::percent(1-(sum(members)/sum(prev_members))))

monthly_churn

})

updatedShareData <- reactive({
  share_data <-share_members_edited %>% 
    filter(earliest_start>=input$ShareTimeRange[1],
           earliest_start<=input$ShareTimeRange[2],
           grepl(input$FreePromoIntro,promo,ignore.case = TRUE),
           grepl(paste0(input$shareChannel,collapse="|"),acquisition_channel),
           grepl(paste0(input$hanaLocation,collapse="|"),hana_location)) 

  return(share_data)
})

updatedShareSurvival<- reactive({
  
#n_days <- interval(input$ShareTimeRange[1],today())/days(1)
n_days <- interval(RiHana::get_relevant_date()$yoy_date,today())/days(1)
cohort_dates<- tibble::enframe(RiHana::get_relevant_date()$yoy_date + days(0:n_days)) %>% 
  mutate(cohort_month=floor_date(value,unit="month"),
         end_month=ceiling_date(value,unit="month")-1) %>% 
  #group_by(cohort_month) %>% 
  select(cohort_month,end_month) %>% 
  unique(.) %>% 
  mutate(end_month=as_date(ifelse(end_month>RiHana::get_relevant_date()$yesterdays_date,RiHana::get_relevant_date()$yesterdays_date,end_month)))

#  group_by(cohort_month) %>% 
#  summarise(days=n())  

  
  
  share_cohort_members<-share_members_edited %>% 
      filter(earliest_start>=input$ShareTimeRange[1],
           earliest_start<=input$ShareTimeRange[2],
           grepl(input$FreePromoIntro,promo,ignore.case = TRUE),
           grepl(paste0(input$shareChannel,collapse="|"),acquisition_channel),
           grepl(paste0(input$hanaLocation,collapse="|"),hana_location)) %>% 
    mutate(last_member_date=coalesce(latest_cancel,today()),
           join_cohort=floor_date(earliest_start,unit='month')) %>% 
    select(coworkerid,join_cohort,last_member_date)

  share_cohorts<-cohort_dates %>% 
  fuzzyjoin::fuzzy_inner_join(.,share_cohort_members,by=c("cohort_month"="join_cohort","end_month"="last_member_date"),match_fun=list(`>=`,`<=`)) %>% 
  group_by(join_cohort,cohort_month) %>% 
  summarise(members=n()) %>% 
  mutate(period=row_number()) %>% 
  select(-cohort_month) %>% 
  ungroup(.) %>% 
  rbind(share_cohort_members %>% group_by(join_cohort) %>% summarise(members=n()) %>% mutate(period=0) %>% ungroup(.)) %>% 
  arrange(period) %>% 
#  pivot_wider(names_from=period,values_from = members,values_fill = list(members=0))
  pivot_wider(names_from=period,values_from = members)

  return(share_cohorts)  


})

updatedSwipeData <- reactive({
  swipe_data <-member_swipe_days %>% 
    filter(earliest_start>=input$ShareTimeRange[1],
           earliest_start<=input$ShareTimeRange[2],
           grepl(input$FreePromoIntro,promo,ignore.case = TRUE),
           grepl(paste0(input$shareChannel,collapse="|"),acquisition_channel),
           grepl(paste0(input$hanaLocation,collapse="|"),hana_location)) %>% 
    group_by(coworkerid) %>% 
    summarise(days=n()) %>% 
    group_by(days) %>% 
    summarise(members=n())

  return(swipe_data)
})

updatedSwipeDataDay <- reactive({
  swipe_data <-member_swipe_days %>% 
    filter(earliest_start>=input$ShareTimeRange[1],
           earliest_start<=input$ShareTimeRange[2],
           grepl(input$FreePromoIntro,promo,ignore.case = TRUE),
           grepl(paste0(input$shareChannel,collapse="|"),acquisition_channel),
           grepl(paste0(input$hanaLocation,collapse="|"),hana_location)) %>% 
    mutate(total_occurences=n()) %>% 
    group_by(swipe_day) %>% 
    summarise(occurences=n()/max(total_occurences))

  return(swipe_data)
})

updatedFirstSharePlans <- reactive({
  share_data <-share_members_edited %>% 
    filter(earliest_start>=input$ShareTimeRange[1],
           earliest_start<=input$ShareTimeRange[2],
           grepl(input$FreePromoIntro,promo,ignore.case = TRUE),
           grepl(paste0(input$shareChannel,collapse="|"),acquisition_channel),
           grepl(paste0(input$hanaLocation,collapse="|"),hana_location)) %>% 
    group_by(first_contract) %>% 
    summarise(members=n()) %>% 
    mutate(share=members/sum(members)) %>% 
    arrange(share) %>% 
  #  mutate(first_contract=forcats::fct_inorder(first_contract))
    mutate(first_contract=forcats::fct_inorder(forcats::fct_lump(first_contract,n=10,w=share)))

  return(share_data)
})

updatedCurrentSharePlans <- reactive({
  share_data <-share_members_edited %>% 
    filter(earliest_start>=input$ShareTimeRange[1],
           earliest_start<=input$ShareTimeRange[2],
           grepl(input$FreePromoIntro,promo,ignore.case = TRUE),
           grepl(paste0(input$shareChannel,collapse="|"),acquisition_channel),
           grepl(paste0(input$hanaLocation,collapse="|"),hana_location),
           still_active=='Yes') %>% 
    mutate(last_contract=ifelse(latest_start>RiHana::get_relevant_date()$yesterdays_date,first_contract,last_contract)) %>% 
    group_by(last_contract) %>% 
    summarise(members=n()) %>% 
    mutate(share=members/sum(members)) %>% 
    arrange(share) %>% 
  #  mutate(first_contract=forcats::fct_inorder(first_contract))
    mutate(last_contract=forcats::fct_inorder(forcats::fct_lump(last_contract,n=10,w=share)))

  return(share_data)
})

updatedShareSources <- reactive({
  source_data <-share_members_edited %>% 
    filter(earliest_start>=input$ShareTimeRange[1],
           earliest_start<=input$ShareTimeRange[2],
           grepl(input$FreePromoIntro,promo,ignore.case = TRUE),
           grepl(paste0(input$shareChannel,collapse="|"),acquisition_channel),
           grepl(paste0(input$hanaLocation,collapse="|"),hana_location)) %>% 
    group_by(acquisition_source) %>% 
    summarise(members=n()) %>% 
    arrange(members) %>% 
    mutate(acquisition_source=forcats::fct_inorder(acquisition_source))
  

  return(source_data)
})

```

Sidebar {.sidebar}
=====================================
###### **Data Updated:** _`r as_date(file.info('inc/share_data.RData')$mtime)` ._

```{r}

dateRangeInput('ShareTimeRange',
      label = 'Choose the time range',
      min=RiHana::get_relevant_date()$yoy_date,
      max=RiHana::get_relevant_date()$yesterdays_date,
      start = RiHana::get_relevant_date()$yoy_date, 
      end = RiHana::get_relevant_date()$yesterdays_date,
      weekstart = 1
    )


selectizeInput(
        'hanaLocation', 'Choose a location', choices = unique(share_members_edited$hana_location),
        options = list(
          placeholder = 'Please select an option below',
          onInitialize = I('function() { this.setValue("*"); }')
        ),
        multiple=TRUE
)

selectizeInput(
        'shareChannel', 'Choose the acquisition channel', choices = unique(share_members_edited$acquisition_channel),
        options = list(
          placeholder = 'Please select an option below',
          onInitialize = I('function() { this.setValue("*"); }')
        ),
        multiple=TRUE
)


radioButtons("FreePromoIntro",label="Filter for free promo",
             choices=c("No"="*",
                       "Yes"="Yes"),
             selected="*")

```

<strong> Cohort Survival</strong> - column 0 represents total number of signups during cohort month.  column 1 represents total number who still have an active plan at the end of the signup month. 2-n are counts of members at the end of referenced month.

<strong>Days in unit (DIU)</strong> - Count of unique days a member has been identified as being at a Hana unit.  Currently using feenics swipe data only.

<strong>Member Utilization</strong> - DIU/Membership Length (in days)




Overview {data-orientation=rows}
===================================== 


Row{ width=8}
-------------------------------------
### Share Members (acquired)

```{r}
my_colors<-hana_color_palette(3)

renderValueBox({
  shareSummary<-updatedShareDataSummary()
valueBox(prettyNum(shareSummary$total_members,big.mark = ","), 
         icon = "fa-user",
         color = "#E6E2DA")
})
```

### Share Members (active)

```{r}
my_colors<-hana_color_palette(3)
renderValueBox({
  shareSummary<-updatedShareDataSummary()
valueBox(prettyNum(shareSummary$active_members,big.mark = ","), 
         icon = "fa-smile",
         color = "#E6E2DA")
})

```

### Average Rev/Member

```{r}
my_colors<-hana_color_palette(3)
renderValueBox({
  shareSummary<-updatedShareDataSummary()
valueBox(prettyNum(shareSummary$rev_member,big.mark = ","), 
         icon = "fa-file-invoice-dollar",
         color = "#E6E2DA")
})
```


### Monthly Member churn

```{r}
my_colors<-hana_color_palette(3)
renderValueBox({
  churnSummary<-updatedShareMonthlyChurn()
valueBox(prettyNum(churnSummary$monthly_churn,big.mark = ","), 
         icon = "fa-sign-out-alt",
         color = "#E6E2DA")
})
```


Row
-------------------------------------

### Cohort Survival

```{r}

DT::renderDataTable({
datatable(updatedShareSurvival(), escape = FALSE,rownames = FALSE, extensions = c('Scroller', 'Buttons'), 
#          options = c(list(scrollY = 800, scroller = TRUE, scrollX=TRUE, deferRender=TRUE, columnDefs = list(list(className = 'dt-left', targets = 0:3))),list(dom='t',ordering=F)))
          options = c(list(scroller = TRUE,scrollY = 300,scrollX=TRUE, deferRender=TRUE, dom='t',ordering=F)))
})
  
```


### Cohort Retention

```{r }

 renderPlotly({

   share_members<-updatedShareData()
   share_members %>% 
  arrange(desc(join_month)) %>% 
  mutate(join_month=factor(as.character(join_month))) %>% 
  group_by(join_month) %>% 
  summarise(retention=sum(still_active=='Yes')/n()) %>% 
  plot_ly(marker = list(color = "#002D36"),
          orientation='h',
          y = ~join_month,
          x = ~retention,
          type="bar") %>% 
     layout(yaxis = list(autorange = "reversed"),
            xaxis= list(tickformat = "%"))
    })   




```



Row
-------------------------------------

### Days in unit

```{r }

renderPlotly({

swipe_data_detail<-updatedSwipeData()
swipe_data_detail %>% 
plot_ly(marker = list(color = "#002D36"),
          orientation='v',
          y = ~members,
          x = ~days,
          type="bar") 
    })     

# density <- density(swipe_data_detail$days)
# plot_ly(x = ~density$x, 
#         y = ~density$y, 
#         type = 'scatter', 
#         mode = 'lines', 
#         fill = 'tozeroy',
#         fillcolor = '#002D36',
#         line = list(width = 0.5)) %>%
#   layout(xaxis = list(title = 'Days on site',
#                       showgrid=F),
#          yaxis = list(title = 'Density'))
#})

```

### Member Utilization

```{r }

renderPlotly({

share_data_detail<-updatedShareData()
  
density <- density(share_data_detail$member_utilization)
plot_ly(x = ~density$x, 
        y = ~density$y, 
        type = 'scatter', 
        mode = 'lines', 
        fill = 'tozeroy',
        fillcolor = '#002D36',
        line = list(width = 0.5)) %>%
  layout(xaxis = list(title = 'Member Usage',
                      showgrid=F,
                      tickformat = "%"),
         yaxis = list(title = 'Relative Probability')) 
})

```


### Day of Week usage

```{r }


 renderPlotly({

  swip_data_detail<-updatedSwipeDataDay()
  swip_data_detail %>%  
  plot_ly(marker = list(color = "#002D36"),
          orientation='v',
          y = ~occurences,
          x = ~swipe_day,
          type="bar") %>% 
    layout(yaxis= list(tickformat = "%"))

    })   


```

Share Customers {data-orientation=rows}
===================================== 

Row
-------------------------------------

### First Plan

```{r }


 renderPlotly({

  share_plan_detail<-updatedFirstSharePlans()
  share_plan_detail %>%  
  plot_ly(marker = list(color = "#002D36"),
          orientation='h',
          y = ~first_contract,
          x = ~share,
          type="bar") %>% 
    layout(xaxis= list(tickformat = "%"))

    })   


```

### Current Active Plans

```{r }


 renderPlotly({

  share_plan_detail<-updatedCurrentSharePlans()
  share_plan_detail %>%  
  plot_ly(marker = list(color = "#002D36"),
          orientation='h',
          y = ~last_contract,
          x = ~share,
          type="bar") %>% 
    layout(xaxis= list(tickformat = "%"))

    })   


```


Row
-------------------------------------

### Acquisition Source


```{r }


 renderPlotly({

  share_source_detail<-updatedShareSources()
  share_source_detail %>%  
  plot_ly(marker = list(color = "#002D36"),
          orientation='h',
          y = ~acquisition_source,
          x = ~members,
          type="bar") 

    })   


```

### Site access by membership length


```{r }


 renderPlotly({

  share_source_detail<-updatedShareData()
  share_source_detail %>%  
  plot_ly(marker = list(color = "#002D36"),
          y = ~membership_length,
          x = ~swipe_days) 

    })   


```


Share Details {data-orientation=rows}
===================================== 

```{r }


DT::renderDataTable({
datatable(updatedShareData(), escape = FALSE,rownames = FALSE, extensions = c('Scroller', 'Buttons'), 
          options = c(list(scrollY = 800, scroller = TRUE, scrollX=TRUE, deferRender=TRUE, dom = 'fBrtip',buttons = c('csv'))))
})

```

